Methodology for Assessing the State of the Practice for Domain X

### 2020-03-20 StateOfPractice/Methodology/Methodology.tex
Update Methodology

@@

Environment 1:
\begin{itemize}
\item Hardware: laptop
\item OS: Windows 10
\item Node.js version: 12
\item npm version: 6
\item Does it work: No
\item Errors: errors during "npm install" step
\end{itemize}

Environment 2:
\begin{itemize}
\item Hardware: Google Cloud VM
\item OS: Ubuntu 18.04
\item Node.js version: 8
\item npm version: 3
\item Does it work: No
\item Errors: errors during "npm install" step
\end{itemize}

Environment 3:
\begin{itemize}
\item Hardware: Google Cloud VM
\item OS: Ubuntu 18.04
\item Node.js version: 8
\item npm version: 6
\item Does it work: Yes
\item Errors: see following tests
\end{itemize}

Test 1 on environment 3: 
\begin{itemize}
\item Repo: 3D Slicer \href{https://github.com/Slicer/Slicer}{Github repo}
\item Command line or web app: web app
\item Quick Analyze checked: Yes
\item Time Consumption: 96s
\item Errors/problems: data of total/open/closed issues are missing, data of
Cyclomatic and Halstead metrics are missing.
\end{itemize}

Test 2 on environment 3: 
\begin{itemize}
\item Repo: 3D Slicer \href{https://github.com/Slicer/Slicer}{Github repo}
\item Command line or web app: web app
\item Quick Analyze checked: No
\item Time Consumption: 4.3hrs
\item Errors/problems: the web app lost response after the analysis
\end{itemize}

Test 3/4 on environment 3: 
\begin{itemize}
\item Ao's repo \href{https://github.com/Ao99/e-commerce-django}{Github
repo}
\item Command line or web app: web app
\item Quick Analyze checked: Yes/No
\item Time Consumption: 121s/117s
\item Errors/problems: most data are missing
\end{itemize}

Test 5/6 on environment 3: 
\begin{itemize}
\item HubListener
\href{https://github.com/pjmc-oliveira/HubListener}{Github repo}
\item Command line or web app: web app
\item Quick Analyze checked: Yes/No
\item Time Consumption: 49s/131s
\item Errors/problems: none
\end{itemize}

>>>>

The data that HubListener can extract.

@@

Test results: HubListener works well on the repo of itself, but it did not work well on some other repos.
